Robust Clustering for Ad Hoc Cognitive Radio Network

### 2017-04-16 journal-draft/ettdoc.tex
comment out ack
modify typos

\begin{abstract}
Cluster structure in cognitive radio networks facilitates cooperative spectrum sensing, routing and other functionalities.
The unlicensed channels which are available for a group of cognitive radio users, consolidate the group into a cluster and the number of the available unlicensed channels decides that cluster's robustness against the licensed users' influence.
This paper analyses the problem of how to form robust clusters in cognitive radio network, so that more cognitive radio users can get the benefits from cluster structure when the primary users' operation becomes more intense.
%In the process of forming clusters, every secondary user decides with whom to form a cluster, or which cluster to join.
We give a formal description of the robust clustering problem, prove it to be NP-hard and propose both centralized and distributed solutions.
The congestion game model is adopted to analyse the process of cluster formation, which not only contributes the design of the distributed clustering scheme, but also provides the guarantee on the convergence into Nash Equilibrium and the convergence speed.
%Our proposed clustering solution is versatile to fulfill some other requirements such as faster convergence and cluster size control.
The proposed distributed clustering scheme outperforms the related works in terms of cluster robustness, convergence speed and overhead.
%Besides, we prove the clustering problem is NP-hard, and also propose the centralized solution.
The extensive simulation is conducted, which clearly supports our claims.
\end{abstract}

@@

\subsubsection{Bridging ROSS-DGA with Congestion Game}
\label{clustering:phaseII:game}
Game theory is a powerful mathematical tool for studying, modelling and analysing the interactions among individuals.
A game consists of three elements: a set of players, a selfish utility for each player, and a feasible strategy space for each player. In a game, the players are rational and intelligent decision makers, which are related with one explicit formalized incentive expression (the utility or cost).
Game theory provides standard procedures to study its equilibriums~\cite{game_for_communication_01}.
In the past few years, game theory has been extensively applied to problems in communication and networking~\cite{Neel06analysisand, Wang_gtc_crn_survey_2010}.
Congestion game is an attractive game model which describes the problem where participants compete for limited resources in a non-cooperative manner, it has the good property that Nash equilibrium can be achieved after finite steps of best response dynamic, \ie each player chooses the strategy to maximize/minimize its utility/cost with respect to the other players' strategies.
The framework of the congestion game has been used to model certain problems in internet-centric applications or cloud computing, where self-interested clients compete for the centralized resources and meanwhile interact with each other.
For example, server selection is involved in distributed computing platforms~\cite{Cloud_Computing_2010}, or users downloading files from cloud, etc.

@@

\subsection{Comparison among the Distributed Schemes}
\label{largeScaleCRN}
In this section we investigate the performances of the proposed distributed clustering schemes in CRN with different network scales and densities.
The transmission range of CR is $A/5$, PU's transmission range is $2A/5$.
The initial number of PU is 30.
%The number of CR is 100, 200 and 300, and the average number of neighbours of each CR is 9.5, 20, and 31.
The desired sizes adopted are listed in the Table~\ref{Simulation_para}, which is about 60\% of the average number of neighbours.
%When run ROSS, the parameter $t$ which is used to control cluster size in phase I is 1.3.

\begin{table}[ht]
\caption{}
\label{Simulation_para}
{\small
%\hfill{}
\begin{tabular}{|L{3 cm}|C{0.85 cm}|C{0.85 cm}|C{0.85 cm}|}
\hline
Number of CRs			& 100 	&  200 					& 300 \\ \hline
Average num. of neighbours 	&9.5	&   20		& 31  \\ \hline
Desired size $\delta$ 	& 6	&   12 						& 20      \\ \hline
\end{tabular}
}
%\hfill{}
\end{table}

@@

\subsubsection{Robustness of the formed clusters}
We increase the primary users' activity by importing 20 batches of PUs sequentially in the CRN, where each batch includes 10 PUs. 
%
Figure~\ref{singleton_clusters_100} and \ref{singleton_clusters_200} show that when $N=100$ and 200, compared with the variants of ROSS, more unclustered CR nodes are generated by SOC.
When $N=300$ as shown in Figure~\ref{singleton_clusters_300} and the new PUs are not many, ROSS-DGA/DFA generate slightly more unclustered CR nodes than SOC, but SOC's performance deteriorates quickly when the PUs continue increasing.
%
From Figure~\ref{singleton_clusters_100} to~\ref{singleton_clusters_300}, we can see that significantly less unclustered CR nodes are generated by the variants of ROSS whcih have size control mechanism.
Besides, the greedy mechanism moderately strengthens the robustness of the clusters.
We only show the average values of the variants of ROSS as their confidence intervals overlap.

@@

% use section* for acknowledgment

@@

%we assume every node has at least one neighbour.
For the sake of contradiction, let us assume there exist a secondary user $\alpha$ which is not included into any cluster.
Then there is at least one node $\beta\in \text{Nb}(\alpha)$ such that $d_{\alpha} > d_{\beta}$ (otherwise $\alpha$ becomes cluster head). 
In this case, according to Algorithm~\ref{alg0}, $\beta$ is not included in any clusters, because otherwise $d_{\beta} = M$, a large positive integer, which contradicts to $d_{\alpha} > d_{\beta}$.
Now, we distinguish between two cases: 
%Otherwise, node $\alpha$ is eligible to form a cluster. COMMENT: unnecessary sentence!
If $\beta$ becomes cluster head, node $\alpha$ is included, the assumption is not true.
If $\beta$ is not a cluster head, then $\beta$ is not in any cluster, we can repeat the previous analysis made on node $\alpha$, and deduce that node $\beta$ has at least one neighbouring node $\gamma$ with $d_{\gamma} < d_{\beta}$.
% (COMMENT: $\beta$ not being a cluster head and $\beta$ not belonging to any cluster is not the same statement!!! ANSWER(Di): I add some more words)
So far, when there is no cluster head identified, the unclustered nodes, \ie $\alpha$, $\beta$ form a linked list, where their connectivity degrees monotonically decrease.
But this list will not continue to grow, because the minimum individual connectivity degree is zero, and the length of this list is upper bounded by the total number of nodes in the CRN.
An example of the formed node series is shown as Figure~\ref{lemma1}.

@@

In this example, node $\omega$ is at the tail of a list.
As $\omega$ does not have neighboring nodes with lower individual connectivity degree, $\omega$ becomes a cluster head.
Then $\omega$ incorporates all its one-hop neighbours (here we assume that every newly formed cluster has common channels), including the nodes which precede $\omega$ in the list.
The nodes which join a cluster set their individual connection degrees to $M$, which makes the node immediately precede in the list to become a cluster head.
In this way, cluster heads are generated from the tail to the head in the list, and every node in the list is in at least one cluster, which contradicts the assumption that $\alpha$ is not included in any cluster.

@@

\ack This class file was developed by Sunrise Setting Ltd,
Paignton, Devon, UK. Website:\\
\href{http://www.sunrise-setting.co.uk}{\texttt{www.sunrise-setting.co.uk}}

>>>>

\begin{abstract}
Cluster structure in cognitive radio networks facilitates cooperative spectrum sensing, routing and other functionality.
The unlicensed channels which are available for a group of cognitive radio users, consolidate the group into a cluster and the number of the available unlicensed channels decides that cluster's robustness against the licensed users' influence.
This paper analyses the problem of how to form robust clusters in cognitive radio network, so that more cognitive radio users can get the benefits from cluster structure when the primary users' operation becomes more intense.
%In the process of forming clusters, every secondary user decides with whom to form a cluster, or which cluster to join.
We give a formal description of the robust clustering problem, prove it to be NP-hard and propose both centralized and distributed solutions.
The congestion game model is adopted to analyze the process of cluster formation, which not only contributes the design of the distributed clustering scheme, but also provides the guarantee on the convergence into Nash Equilibrium and the convergence speed.
%Our proposed clustering solution is versatile to fulfill some other requirements such as faster convergence and cluster size control.
The proposed distributed clustering scheme outperforms the related works in terms of cluster robustness, convergence speed and overhead.
%Besides, we prove the clustering problem is NP-hard, and also propose the centralized solution.
The extensive simulation is conducted, which clearly supports our claims.
\end{abstract}

@@

\subsubsection{Bridging ROSS-DGA with Congestion Game}
\label{clustering:phaseII:game}
Game theory is a powerful mathematical tool for studying, modeling and analyzing the interactions among individuals.
A game consists of three elements: a set of players, a selfish utility for each player, and a feasible strategy space for each player. In a game, the players are rational and intelligent decision makers, which are related with one explicit formalized incentive expression (the utility or cost).
Game theory provides standard procedures to study its equilibriums~\cite{game_for_communication_01}.
In the past few years, game theory has been extensively applied to problems in communication and networking~\cite{Neel06analysisand, Wang_gtc_crn_survey_2010}.
Congestion game is an attractive game model which describes the problem where participants compete for limited resources in a non-cooperative manner, it has the good property that Nash equilibrium can be achieved after finite steps of best response dynamic, \ie each player chooses the strategy to maximize/minimize its utility/cost with respect to the other players' strategies.
The framework of the congestion game has been used to model certain problems in internet-centric applications or cloud computing, where self-interested clients compete for the centralized resources and meanwhile interact with each other.
For example, server selection is involved in distributed computing platforms~\cite{Cloud_Computing_2010}, or users downloading files from cloud, etc.

@@

\subsection{Comparison among the Distributed Schemes}
\label{largeScaleCRN}
In this section we investigate the performances of the proposed distributed clustering schemes in CRN with different network scales and densities.
The transmission range of CR is $A/5$, PU's transmission range is $2A/5$.
The initial number of PU is 30.
%The number of CR is 100, 200 and 300, and the average number of neighbours of each CR is 9.5, 20, and 31.
The desired sizes adopted are listed in the Table~\ref{Simulation_para}, which is about 60\% of the average number of neighbors.
%When run ROSS, the parameter $t$ which is used to control cluster size in phase I is 1.3.

\begin{table}[ht]
\caption{}
\label{Simulation_para}
{\small
%\hfill{}
\begin{tabular}{|L{3 cm}|C{0.85 cm}|C{0.85 cm}|C{0.85 cm}|}
\hline
Number of CRs			& 100 	&  200 					& 300 \\ \hline
Average num. of neighbors 	&9.5	&   20		& 31  \\ \hline
Desired size $\delta$ 	& 6	&   12 						& 20      \\ \hline
\end{tabular}
}
%\hfill{}
\end{table}

@@

\subsubsection{Robustness of the formed clusters}
We increase the primary users' activity by importing 20 batches of PUs sequentially in the CRN, where each batch includes 10 PUs. 
%
Figure~\ref{singleton_clusters_100} and \ref{singleton_clusters_200} show that when $N=100$ and 200, compared with the variants of ROSS, more unclustered CR nodes are generated by SOC.
When $N=300$ as shown in Figure~\ref{singleton_clusters_300} and the new PUs are not many, ROSS-DGA/DFA generate slightly more unclustered CR nodes than SOC, but SOC's performance deteriorates quickly when the PUs continue increasing.
%
From Figure~\ref{singleton_clusters_100} to~\ref{singleton_clusters_300}, we can see that significantly less unclustered CR nodes are generated by the variants of ROSS which have size control mechanism.
Besides, the greedy mechanism moderately strengthens the robustness of the clusters.
We only show the average values of the variants of ROSS as their confidence intervals overlap.

@@

@@

%we assume every node has at least one neighbour.
For the sake of contradiction, let us assume there exist a secondary user $\alpha$ which is not included into any cluster.
Then there is at least one node $\beta\in \text{Nb}(\alpha)$ such that $d_{\alpha} > d_{\beta}$ (otherwise $\alpha$ becomes cluster head). 
In this case, according to Algorithm~\ref{alg0}, $\beta$ is not included in any clusters, because otherwise $d_{\beta} = M$, a large positive integer, which contradicts to $d_{\alpha} > d_{\beta}$.
Now, we distinguish between two cases: 
%Otherwise, node $\alpha$ is eligible to form a cluster. COMMENT: unnecessary sentence!
If $\beta$ becomes cluster head, node $\alpha$ is included, the assumption is not true.
If $\beta$ is not a cluster head, then $\beta$ is not in any cluster, we can repeat the previous analysis made on node $\alpha$, and deduce that node $\beta$ has at least one neighboring node $\gamma$ with $d_{\gamma} < d_{\beta}$.
% (COMMENT: $\beta$ not being a cluster head and $\beta$ not belonging to any cluster is not the same statement!!! ANSWER(Di): I add some more words)
So far, when there is no cluster head identified, the unclustered nodes, \ie $\alpha$, $\beta$ form a linked list, where their connectivity degrees monotonically decrease.
But this list will not continue to grow, because the minimum individual connectivity degree is zero, and the length of this list is upper bounded by the total number of nodes in the CRN.
An example of the formed node series is shown as Figure~\ref{lemma1}.

@@

In this example, node $\omega$ is at the tail of a list.
As $\omega$ does not have neighboring nodes with lower individual connectivity degree, $\omega$ becomes a cluster head.
Then $\omega$ incorporates all its one-hop neighbors (here we assume that every newly formed cluster has common channels), including the nodes which precede $\omega$ in the list.
The nodes which join a cluster set their individual connection degrees to $M$, which makes the node immediately precede in the list to become a cluster head.
In this way, cluster heads are generated from the tail to the head in the list, and every node in the list is in at least one cluster, which contradicts the assumption that $\alpha$ is not included in any cluster.

@@

%\ack This class file was developed by Sunrise Setting Ltd,
%Paignton, Devon, UK. Website:\\
%\href{http://www.sunrise-setting.co.uk}{\texttt{www.sunrise-setting.co.uk}}
